---
title: "Activity 2.2 - Exploratory Data Analysis: Grouped Summarizing and Manipulating"
author: Purple
date: 09/10/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(gapminder)
```

### Load data

```{r load-data, message=FALSE}
(my_gm <- gapminder)
```


### Exercise 1

| Variable      |Description    |
| ------------- |:-------------:| 
| Country       |Country of origin|
| Continent     |Continent country is in|
| Year          |ranges from 1952 to 2007 in increments of 5 years|
| lifeExp       |life expectancy at birth, in years|
| Pop           |The population|
| GPD per capita|Measured in US$, inflation-adjusted|
### Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...

### Exercise 8

...

### Exercise 9

...
